Lab News

### 2024-10-02 index.qmd
update news

<font color="#d08770">[January 22 2024].</font> **Paper accepted**. Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. [https://doi.org/10.1016/j.neuroscience.2024.01.004](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank"}

<font color="#d08770">[September 22 2023].</font> **New award**. Congratulations to Daniel Deletsu who was awarded a 2-year Master's scholarship through an initiative from the Heart and Stroke Foundation of Canada, Brain Canada Foundation, and the Canadian Institutes of Health Research.

<font color="#d08770">[September 6 2023].</font> **Paper accepted**. Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. [https://doi.org/10.1098/rspb.2023.1475](https://doi.org/10.1098/rspb.2023.1475){target="_blank"}

<font color="#d08770">[August 28 2023].</font> **New members**. Welcome to Daniel Deletsu and Jiaqiao (Jack) Tang. Daniel will be starting his M.Sc in the lab and Jack will be starting his Ph.D in the lab.

<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.

>>>>

<font color="#d08770">[September 18 2024].</font> **Paper accepted**. Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A. Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease. *PLoS Computational Biology*.

<font color="#d08770">[September 05 2023].</font> **New milestone**. Congratulations to Mikayla Lalli on successfully defending her MSc work. We are excited that Mikayla is staying in the lab for her doctoral studies.

<font color="#d08770">[September 03 2024].</font> **Paper accepted**. St. Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*.

<font color="#d08770">[August 20 2024].</font> **New Preprint**. Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A. Online movements reflect ongoing deliberation. *bioR$\chi$iv*. [https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}

### 2024-10-02 join.qmd
update news

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab@mcmaster.ca.

>>>>

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11@mcmaster.ca.

### 2024-10-02 news.qmd
new paper accepted as news
update news

>>>>

<font color="#d08770">[September 18 2024].</font> **Paper accepted**. Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A. Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease. *PLoS Computational Biology*.

<font color="#d08770">[September 05 2023].</font> **New milestone**. Congratulations to Mikayla Lalli on successfully defending her MSc work. We are excited that Mikayla is staying in the lab for her doctoral studies.

<font color="#d08770">[September 03 2024].</font> **Paper accepted**. St. Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*.

<font color="#d08770">[August 20 2024].</font> **New Preprint**. Calalo, J.A., Ngo, T.T., Sullivan, S.R., Strand, K., Buggeln, J.H., Lokesh, R., Roth, A.M., Carter, M.J, Kurtzer, I.L., & Cashaback, J.G.A. Online movements reflect ongoing deliberation. *bioR$\chi$iv*. [https://doi.org/10.1101/2024.08.19.608669](https://doi.org/10.1101/2024.08.19.608669){target="_blank"}

<font color="#d08770">[April 12 2024].</font> **Paper accepted**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the attentional focus literature. *Psychological Bulletin*.
